### 2015-12-02 paper.tex
Move comment to issue #17
Address Budi's comments on tare measurements

    \caption{{\bf Experimental setup.} Illustration of the experimental setup.}
    \textbf{\textit{[would be good to indicate the water surface with text of drawing ( e.g. a triangle and three lines]}}
    \label{fig:exp-setup}
\end{figure}

@@

\paragraph{Tare drag and torque compensation.} Tare torque and drag runs were
performed to measure the shaft bearing friction torque and turbine mounting
frame drag, respectively \textbf{\textit{[explain the purpose of these measurements; how the final drag and torque data were compensated using the tare measurements]}}. Tare drag runs were performed for each tow speed in
the experiment, for which the mean value was used in data processing\textbf{\textit{[describe how this was done - without blades but shaft?]}}. Tare
torque runs were performed by rotating the turbine shaft (without blades) in air
at constant angular velocity for a specified duration, over the range of angular
velocities used throughout the experiment. Tare torque was fit with a linear
regression versus shaft angular velocity, and added to the measured turbine
torque in post-processing.

>>>>

    \caption{{\bf Experimental setup.} Illustration of the experimental setup.}

    \label{fig:exp-setup}
\end{figure}

@@

\paragraph{Tare drag and torque compensation.} To best estimate the hydrodynamic
loads on the turbine rotor alone, tare torque and drag runs were performed to
measure the shaft bearing friction torque and turbine mounting frame drag,
respectively. Tare drag runs---measured with the turbine removed---were
performed for each tow speed in the experiment, for which the mean value was
subtracted in data processing, to arrive at an estimate for drag on the turbine
alone. Tare torque runs were performed by rotating the turbine shaft (without
blades) in air at constant angular velocity for a specified duration, over the
range of angular velocities used throughout the experiment. Tare torque was fit
with a linear regression versus shaft angular velocity, and added to the
measured turbine torque in post-processing.
